---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# invertiforms

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/RoheLab/invertiforms/branch/master/graph/badge.svg)](https://codecov.io/gh/RoheLab/invertiforms?branch=master)
[![R-CMD-check](https://github.com/RoheLab/invertiforms/workflows/R-CMD-check/badge.svg)](https://github.com/RoheLab/invertiforms/actions)
[![CRAN status](https://www.r-pkg.org/badges/version/invertiforms)](https://CRAN.R-project.org/package=invertiforms)
<!-- badges: end -->

The goal of invertiforms is to ...

composable transformations. could have a sparse matrix representing a graph, first row and column center it, then find the graph Laplacian of the centered matrix, decompose that matrix, and then use inverse transformations to inverse transform the results back to the original scale

probably most useful for you is the quick graph Laplacian formation

## Installation

You can install the released version of invertiforms from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("invertiforms")
```

```{r}
library(invertiforms)

library(igraph)
library(igraphdata)

data("karate", package = "igraphdata")

A <- get.adjacency(karate)

iform <- NormalizedLaplacian(A)

L <- transform(iform, A)
L

A_recovered <- inverse_transform(iform, L)

all.equal(A, A_recovered)
```



## composable

## Current transforms

- row center
- column center
- double center
- normalized graph laplacian
- regularized graph laplacian
- perturbed graph laplacian



## related work

- separate transformer based objects like recipes
- Incomplete S4 class in softImpute

