---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# invertiforms

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Codecov test coverage](https://codecov.io/gh/RoheLab/invertiforms/branch/master/graph/badge.svg)](https://codecov.io/gh/RoheLab/invertiforms?branch=master)
[![R build status](https://github.com/RoheLab/invertiforms/workflows/R-CMD-check/badge.svg)](https://github.com/RoheLab/invertiforms/actions)
<!-- badges: end -->

The goal of invertiforms is to ...

## Installation

You can install the released version of invertiforms from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("invertiforms")
```

```{r}
library(jiandjindata)

citation_graph

A <- igraph::get.adjacency(citation_graph)

L <- normalized_graph_laplacian(A)
transform(L)

str(L)

invert(transform(L), L)

all.equal(A, invert(transform(L), L))
```



## composable

## Current transforms

- row center
- column center
- double center
- normalized graph laplacian
- regularized graph laplacian
- perturbed graph laplacian



## related work

- separate transformer based objects like recipes
- Incomplete S4 class in softImpute

